### 2023-03-14 resilience.tex
Separating theorem in three

\begin{theorem}\label{up-up}
The three %uniform 
resilience problems are decidable for WSTS with effective predbasis, $Safe=\uparrow Safe$
and $BAD=\uparrow BAD$.
%	and bad is upward closed or downward closed.
\end{theorem}

\begin{proof}
Let us first solve if $\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(bad,Safe)-resilient. Since $Safe=\uparrow Safe$, and WSTS, $\pred^*(Safe)=\uparrow \pred^*(Safe)$, so $\pred^*(Safe)$ admits a finite basis $B_{\pred^*(Safe)}$. since WSTS  with effective predbasis, we may compute a finite basis of $\pred^*(Safe)$ with the backward coverability algorithm. 
%Then if bad is upward closed or downward closed, we may decide the inclusion $Bad \subseteq \uparrow B_{\pred^*(Safe)}$ which remais to compare, in both cases, two finite sets. 
if bad  is upward closed, $bad = \uparrow B_{bad}$ and $ \uparrow B_{bad} \subseteq \uparrow B_{\pred^*(Safe)}$ iff for every $b \in B_{bad}$, there is a $s \in B_{\pred^*(Safe)}$ such that $s \leq b$. 
\iffalse
similar reasonning for the other case.
\fi
hence the two %uniform
 resilience problems are decidable.

Let us examine the %uniform 
$k$-resilience problem (kRP). We may compute the least $n$ such that $bad \subseteq \uparrow \pred^n(Safe)=  \uparrow \pred^*(Safe)$. $S$ is %uniformely 
$k$-resilient iff $n \leq k$ \alain{hum...mais il peut y avoir des chemins plus courts}
\mathieu{Si on a la résilience alors on a la $k$-résilience pour les $k$ plus grands que le $n$ minimal tel que $\uparrow \pred^n(Safe)=  \uparrow \pred^*(Safe)$, mais il faut traiter aussi les $k$ plus petits.}
\mathieu{Si on a $\uparrow \pred^k(Safe) = \pred^k(Safe)$ on résoud comme ci-dessus.}
\mathieu{... mais pour les $k$ plus petits, on peut avoir $\uparrow \pred^k(Safe) \neq \pred^k(Safe)$.}
\mathieu{... et alors, c'est plus compliqué.}
\mathieu{L'important c'est d'avoir le $n$ minimal tel que $bad \subseteq \pred^n(Safe)$, qui n'est pas forcément tel que $\uparrow \pred^n(Safe)=  \uparrow \pred^*(Safe)$.}and then kRP is decidable.
\end{proof}

>>>>

\begin{theorem}\label{up-up}
The % three %uniform 
resilience problems is decidable for WSTS with effective predbasis, $Safe=\uparrow Safe$
and $BAD=\uparrow BAD$.
%	and bad is upward closed or downward closed.
\end{theorem}

\begin{proof}
Let us first solve if $\mathscr{S}=(S,\rightarrow,\leq)$ is %uniformely 
(bad,Safe)-resilient. Since $Safe=\uparrow Safe$, and WSTS, $\pred^*(Safe)=\uparrow \pred^*(Safe)$, so $\pred^*(Safe)$ admits a finite basis $B_{\pred^*(Safe)}$. since WSTS  with effective predbasis, we may compute a finite basis of $\pred^*(Safe)$ with the backward coverability algorithm. 
%Then if bad is upward closed or downward closed, we may decide the inclusion $Bad \subseteq \uparrow B_{\pred^*(Safe)}$ which remais to compare, in both cases, two finite sets. 
if bad  is upward closed, $bad = \uparrow B_{bad}$ and $ \uparrow B_{bad} \subseteq \uparrow B_{\pred^*(Safe)}$ iff for every $b \in B_{bad}$, there is a $s \in B_{\pred^*(Safe)}$ such that $s \leq b$. 
\iffalse
similar reasonning for the other case.
\fi
hence the %two
 %uniform
 resilience problems is decidable.
\end{proof}

\begin{corollary}
The bounded resilience problems is decidable for WSTS with effective predbasis, $Safe=\uparrow Safe$
and $BAD=\uparrow BAD$.
\end{corollary}

\begin{theorem}\label{up-up}
The % three %uniform 
$k$-resilience problems is decidable for WSTS with effective predbasis, $Safe=\uparrow Safe$
and $BAD=\uparrow BAD$.
%	and bad is upward closed or downward closed.
\end{theorem}

\begin{proof}
Let us examine the %uniform 
$k$-resilience problem (kRP). We may compute the least $n$ such that $bad \subseteq \uparrow \pred^n(Safe)=  \uparrow \pred^*(Safe)$. $S$ is %uniformely 
$k$-resilient iff $n \leq k$ \alain{hum...mais il peut y avoir des chemins plus courts}
\mathieu{Si on a la résilience alors on a la $k$-résilience pour les $k$ plus grands que le $n$ minimal tel que $\uparrow \pred^n(Safe)=  \uparrow \pred^*(Safe)$, mais il faut traiter aussi les $k$ plus petits.}
\mathieu{Si on a $\uparrow \pred^k(Safe) = \pred^k(Safe)$ on résoud comme ci-dessus.}
\mathieu{... mais pour les $k$ plus petits, on peut avoir $\uparrow \pred^k(Safe) \neq \pred^k(Safe)$.}
\mathieu{... et alors, c'est plus compliqué.}
\mathieu{L'important c'est d'avoir le $n$ minimal tel que $bad \subseteq \pred^n(Safe)$, qui n'est pas forcément tel que $\uparrow \pred^n(Safe)=  \uparrow \pred^*(Safe)$.}and then kRP is decidable.
\end{proof}
